Appendix A: Code and supplementary figures for simulation and policy analyis

### 2018-01-30 appendix/appendixA.Rmd
fix typo

The POMDP calculations presented here are performed using the `sarsop` R package, which we have written to provide a general purpose implementation of the SARSOP algorithm of @Kurniawati2008. The version used in this analysis can be installed from GitHub using the command: `devtools::install_github("boettiger-lab/sarsop@v0.5.0")`.

```{r library, message=FALSE}
devtools::install_github("boettiger-lab/sarsop@v0.5.0")
library(sarsop)       # Our main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)     
library(gridExtra)
```

@@

```{r overest}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source(system.file("examples/pomdp_overestimate.R", package="sarsop")) # portable example code
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario"
  )
```

>>>>

The POMDP calculations presented here are performed using the `sarsop` R package, which we have written to provide a general purpose implementation of the SARSOP algorithm of @Kurniawati2008. The version used in this analysis can be installed from GitHub using the command: `devtools::install_github("boettiger-lab/sarsop@0.5.0")`.

```{r library, message=FALSE}
#devtools::install_github("boettiger-lab/sarsop@0.5.0")
library(sarsop)       # Our main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)     
library(gridExtra)
```

@@

```{r overest}
set.seed(12345)
true <- 3 # sigma_g = 0.15, sigma_m = 0
source(system.file("examples/pomdp_overestimates.R", package="sarsop")) # portable example code
pomdp_overest_sims <- 
  map2_dfr(models, alphas, function(.x, .y){
    pomdp_overestimates(transition = .x$transition, 
            model_observation = .x$observation, 
            reward = .x$reward, 
            discount = discount, 
            true_observation = models[[true]]$observation,
            x0 = x0,
            Tmax = Tmax,
            alpha = .y,
            reps = reps)$df %>% 
              mutate(method = "POMDP") # include a column labeling method
           },
           .id = "scenario"
  )
```
